### 2019-06-15 papers/journal/conclusion.tex

To conclude, we have established a connection between vesicle transport graph connectedness and underlying rules of SNARE pairing and regulation. 
%
The constraints implied by SNARE protein properties translates into
mathematically elegant properties of the transport graph, namely its connectivity.
%
Our approach demonstrates the power of SMT solvers in a {\em novel} application and the value of careful encoding of the problems into SMT queries. 
We manage to scale the tool up to the size that makes the tool biologically relevant.
%

However, the problem of searching for all $k$-connected VTSs induces quantifier alternation in the encodings.
%
Therefore, a simple call to SAT solver may not work efficiently. 
%
We used QBF solvers for such queries.
%
Our connectivity results contain many predictions which can in principle be tested through cell-biological experiments. 
%
One may also be interested in counting the number of graphs that satisfy
a given property. 
%
Exact counting of the graphs using SAT solvers may prove to be very
difficult. 
%
We are planning to employ approximate counting methods for finding the solution.
%
%Our results contain many predictions which can in principle be tested through cell-biological experiments.

>>>>

\noindent 
To conclude, we have established a connection between vesicle transport graph connectedness and underlying rules of SNARE pairing and regulation. 
%
The constraints implied by SNARE protein properties translates into
mathematically elegant properties of the transport graph, namely its connectivity.
%
Our approach demonstrates the power of SMT solvers in a {\em novel} application and the value of careful encoding of the problems into SMT queries. 
We manage to scale the tool up to the size that makes the tool biologically relevant.
%

However, the problem of searching for all $k$-connected VTSs induces quantifier alternation in the encodings.
%
Therefore, a simple call to SAT solver may not work efficiently. 
%
We used QBF solvers for such queries.
%
Our connectivity results contain many predictions which can in principle be tested through cell-biological experiments. 
%
One may also be interested in counting the number of graphs that satisfy
a given property. 
%
Exact counting of the graphs using SAT solvers may prove to be very
difficult. 
%
We are planning to employ approximate counting methods for finding the solution.
%
